The Inconsistency in G\"odel's Ontological Argument: \\ A Success Story for AI in Metaphysics

### 2016-04-13 Papers/InProgress/IJCAI/main.tex
moved file

\title{The Inconsistency in G\"odel's Ontological Argument: \\ A Success Story for AI in Metaphysics}
\author{
  \begin{minipage}{0.5\textwidth}\centering
    Christoph Benzm\"uller\thanks{This work was supported by the 
                                  German National Research Foundation (DFG) under
                                  grants BE 2501/9-1 and BE 2501/11-1.} \\
    \normalfont Freie Universit\"at Berlin \& Stanford University\\
    c.benzmueller@gmail.com
  \end{minipage}
  \begin{minipage}{0.5\textwidth}\centering
    Bruno Woltzenlogel Paleo \\
    \normalfont Australian National University\\
    bruno.wp@gmail.com
  \end{minipage}
}

>>>>

\title{The Inconsistency in G\"odel's Ontological Argument: \\ A Success Story for AI in Metaphysics}
\author{
  \begin{minipage}{0.5\textwidth}\centering
    Christoph Benzm\"uller\thanks{This work was supported by the 
                                  German National Research Foundation (DFG) under
                                  grants BE 2501/9-2 and BE 2501/11-1.} \\
    \normalfont Freie Universit\"at Berlin \& Stanford University\\
    c.benzmueller@gmail.com
  \end{minipage}
  \begin{minipage}{0.5\textwidth}\centering
    Bruno Woltzenlogel Paleo \\
    \normalfont Australian National University\\
    bruno.wp@gmail.com
  \end{minipage}
}
